Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Complete another paper inside the related work section

%TODO: modify here
One other type of information that could be extracted and used for valuable
purposes is the summary of a bug report, as shown in the work of 
Rastkar et. al \cite{rastkar2010summarizing}. The authors wanted to determine if bug reports
could be summarized effectively and automatically so that developers would
need only analyze summaries instead of full tickets. Firstly, they asked
university students to volunteer to annotate the bug reports collected from
various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
a summary of maximum 250 words in their own sentences. These human-produced 
annotations were then used by algorithms to learn how to effectively summarize a 
bug report.  Afterwards, the authors asked the end users of these bug reports, the 
software developers, to rate the summaries against the original bug reports.
They eventually learned that existing conversation-based extractive summary
generators trained on bug reports produce the best results.

We tried to apply the technique presented in the work of Fischer et. al \cite{fischer2003analyzing},
where they present a way to track specific version controlled branches from information
in software tickets.  They managed to successfully visualize the tracked features and illustrate 
their non apparent dependencies which can prove very useful in projects with a large number of
components.

@@

However, bug report assignment is not the only part of bug triaging that needs
investigation. Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
can predict the severity of a reported bug (i.e. assign story points to the 
ticket) automatically. The authors conducted their research on the Mozilla,
Eclipse and GNOME projects and divided their method into four steps:
  \begin{itemize}
    \item extract and organize bug reports;
    \item pre-process bug reports - tokenization, stop word removal and stemming;
    \item train the classifier on multiple datasets of bug reports - 70\% 
      training and 30\% evaluation;
    \item apply the trained classifier on the evaluation set.
  \end{itemize}
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as deadlock, hand, crash, memory or segfault usually indicate
      a severe bug; however, there are other terms that can indicate the opposite,
      such as typos;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large dataset in order to predict correctly;
    \item depending on how well a software project is componentized, one can 
      use a predictor per component rather than an universal one.
  \end{itemize}

>>>>

The first information to be filled in by end users or developers on any issue tracking system
is the summary field, which holds a small description, usually between 5 and 30 words, of 
the request or bug being reported. In the study conducted by Rastkar et. al \cite{rastkar2010summarizing}, 
the authors investigated whether tickets could be summarized automatically and efficiently. What 
that implies is that developers would not be required to look at complete tickets comprised 
of a large number of fields, but rather at a simple summary of a couple of lines 
encapsulating the whole information. The authors selected the Mozilla, Eclipse, Gnome and KDE 
open source projects and then they asked volunteering university students to annotate 
the tickets in the issue tracking systems. More specifically, they had to write a summary 
of maximum 250 words using both technical and non-technical terms, depending on their expertise. 
Then, the study presents Machine Learning algorithms employed to parse these summaries and 
learn how to efficiently create automated summaries for new bug reports. Afterwards, they asked 
software developers to rate these auto-generated summaries against the original ones and 
the conclusion was that existing conversation-based extractive summary generators used 
for software tickets produce the best results.

@@

Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
can predict the severity of a reported bug (i.e. assign story points to the 
ticket) automatically. The authors conducted their research on the Mozilla,
Eclipse and GNOME projects and divided their method into four steps:
  \begin{itemize}
    \item extract and organize bug reports;
    \item pre-process bug reports - tokenization, stop word removal and stemming;
    \item train the classifier on multiple datasets of bug reports - 70\% 
      training and 30\% evaluation;
    \item apply the trained classifier on the evaluation set.
  \end{itemize}
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as deadlock, hand, crash, memory or segfault usually indicate
      a severe bug; however, there are other terms that can indicate the opposite,
      such as typos;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large dataset in order to predict correctly;
    \item depending on how well a software project is componentized, one can 
      use a predictor per component rather than an universal one.
  \end{itemize}
